Transition from forest to agriculture in the Brazilian Amazon from 1985 to 2021

### 2022-11-21 manuscript/manuscript.Rmd
Add some references and TODOs in the results.

Brazil policies since the 1960s were focused on the expansion of the frontier in the Amazon, specially focused in economic income and land security [@Carvalho2002; @Mcdonald2003; @Banerjee2009]. Such development model led to the construction of thousands of kilometers of roads, and the settlement of large scale livestock farms [@Carvalho2002; @Banerjee2009]. This period was marked with high rates of deforestation of mature forests [@Fearnside2005]. At the same time, cattle and soybean productions started to move to the north direction in the Brazilian territory, in which soybeans cultivation areas followed cattle ranches expansion over the Amazon forest [@Simon2005]. This pattern of extensive livestock occupation after deforestation, followed by the establishment of annual crops is very characteristics in the Amazon biome, and persists nowadays. This process can take several decades to be accomplished, or even less than one year, in which it may be considered as a direct transition from forest to agriculture.

@@

TODO: confront our results with Morton 2006 (see the year of 2003).

@@

Interference due to atmospheric conditions and lack of image availability clearly shaped spatial patterns of transitions at some locations. Quality of composites trough the time series affected accuracy of results.

>>>>

Brazil policies since the 1960s were focused on the expansion of the frontier in the Amazon, specially focused in economic income and land security [@Carvalho2002; @Mcdonald2003; @Banerjee2009]. Such development model led to the construction of thousands of kilometers of roads, and the settlement of large scale livestock farms [@Carvalho2002; @Banerjee2009]. This period was marked with high rates of deforestation of mature forests [@Fearnside2005]. At the same time, cattle and soybean productions started to move to the north direction in the Brazilian territory, in which soybeans cultivation areas followed cattle ranches expansion over the Amazon forest [@Simon2005; @Barona2010; @Arima2011]. This pattern of extensive livestock occupation after deforestation, followed by the establishment of annual crops is very characteristic in the Amazon biome, and persists nowadays. This process can take several decades to be accomplished, or even less than one year, in which it may be considered as a direct transition from forest to agriculture.

@@

TODO: confront our results with Morton 2006 (see the year of 2003). Confront results from [@Macedo2012], talking about how the expansion of soybean areas are still responsible for production growth, because of very slow transitions.

TODO: talk that even with soy moratorium, and that the deforestation related to transitions were smaller, the deforestation related to pasture occupation kept going, with indirect effects of soybean expansion (Arima 2011).

@@

Interference due to atmospheric conditions and lack of image availability clearly shaped spatial patterns of transitions at some locations. Quality of composites trough the time series affected accuracy of results. Regions of the North part of the Amazon presents lower quality than regions in the South of the Amazon BIome.
